A Switching Planner for Combined Task and Observation Planning

### 2011-02-08 subarchitectures/planner.sa/trunk/src/latex/AAAI11/dtpddl.tex
removed too large footnote removed comments from pddl examples

%% BEGIN SCRAPPY

%% deal with POND and the Perseus language

%% For example, the robot usually knows exactly where it is located on a
%% topological map, and therefore there are tight constraints about what
%% regions of the map can be observed, and what regions of the map can be
%% moved to in an atomic step.

%% Moreover, we use this domain description to model the action physics
%% of abstract processes posed to decision-theoretic planning
%% sessions. Here, we forbid the planner from considering courses of
%% action that are not {\em known} to be possible to alleviate the
%% computational burden planning in the abstract process.

%% END SCRAPPY

We give an overview of the declarative first-order language DTPDDL, an
extension of PPDDL that can express probabilistic models of the
sensing consequences of acting, to quantitatively capture
unreliability in perception. There are straightforward compilations
from problems expressed in DTPDDL to flat (and factored)
representations of the underlying decision processes. Although similar
to Bryce's POND input language, DTPDDL distinguishes itself by
explicitly treating state and perceptual symbols separately, and by
providing distinct declarations for operators (i.e, state model) and
senses (i.e., observation model). In this last respect, DTPDDL admits
more compact domain descriptions where sensing effects are common
across multiple actions. In detail, DTPDDL has perceptual analogues of
fluent and predicate symbols. For example our {\em object search}
domains have:

\vspace{-1ex}
\small
\begin{tabtt}
(\=:functions  ;; state fluents\\
  \> (is-in ?v - visual-object) - location )\\
(:perceptual-functions  ;; perceptual fluents\\
  \> (o-is-in ?v - visual-object) - location )
\end{tabtt}
\normalsize
\vspace{-1ex}

\noindent Where the first fluent symbol models the actual location of
objects, and the second the instantaneous sensing of objects
following application of an action with sensing consequences.
%%
To model sensing capabilities, we have operator-like declarations,
with preconditions expressed using state and action symbols, and
uniformly positive effects over perceptual symbols. For example, where
{\em look-for-object} is the operator that applies an object detection
algorithm at a specific place, in a simplified {\em object search} task
we have:

@@

@@

If a dual is executed, then the sequential planner must
replan with $\bstate_0$ equal to the underlying
belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
executed, then the current sequential plan is executed until further
sensing is scheduled, or to completion.

@@

>>>>

We give an overview of the declarative first-order language DTPDDL, an
extension of PPDDL that can express probabilistic models of the
sensing consequences of acting, to quantitatively capture
unreliability in perception. There are straightforward compilations
from problems expressed in DTPDDL to flat (and factored)
representations of the underlying decision process. Although similar
to Bryce's POND input language, DTPDDL distinguishes itself by
explicitly treating state and perceptual symbols separately, and by
providing distinct declarations for operators (i.e, state model) and
senses (i.e., observation model). In this last respect, DTPDDL admits
more compact domain descriptions where sensing effects are common
across multiple operators. In detail, DTPDDL has perceptual analogues of
fluent and predicate symbols. For example, a simple {\em object search}
domain would have:

\vspace{-1ex}
\small
\begin{tabtt}
(\=:functions\\
  \> (is-in ?v - visual-object) - location )\\
(:perceptual-functions\\
  \> (o-is-in ?v - visual-object) - location )
\end{tabtt}
\normalsize
\vspace{-1ex}

\noindent Where the first fluent symbol models the actual location of
objects, and the second the instantaneous sensing of objects
following application of an action with sensing consequences.
%%
To model sensing capabilities, we have operator-like ``sense''
declarations, with preconditions expressed using state and action
symbols, and uniformly positive effects over perceptual symbols. For
example, where {\em look-for-object} is the operator that applies an
object detection algorithm at a specific place, an {\em
object search} task will have:

@@

\noindent I.e., there is a 10\% {\em false positive} rate, and 20\%
  probability of a {\em false negative}.

@@

%% If a dual is executed, then the sequential planner must
%% replan with $\bstate_0$ equal to the underlying
%% belief-state. Otherwise, if $\actions.\poss(\switchAction)$ is
%% executed, then the current sequential plan is executed until further
%% sensing is scheduled, or to completion.

@@

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "aaai11"
%%% End:
